Dissertation

### 2024-10-12 Manuscript/manuscript_full.qmd
fix citation and url colors to be black

      # Citations and links
    # lot: true
    # lof: true
    colorlinks: true
    linkcolor: DarkSlateBlue
    urlcolor: DarkSlateBlue
    citecolor: DarkSlateBlue
    link-citations: true
    # linestretch: 1.05
    include-in-header:
      # The \everydisplay thing makes all math blocks use \small font
      text: |
        \usepackage{mathtools}
        \everydisplay\expandafter{\the\everydisplay\small}
        \usepackage{float}
        \floatplacement{figure}{H}
        \floatplacement{table}{H}
        \usepackage{setspace}
        \pagenumbering{arabic}
        \usepackage{titlesec}
        \titleformat{\section}{\fontsize{12}{14}\bfseries}{\thesection}{1em}{}
        \titleformat{\subsection}{\fontsize{11}{14}\bfseries}{\thesubsection}{1em}{}
---

>>>>

      # Citations and links
    # lot: true
    # lof: true
    colorlinks: true
    linkcolor: Black
    urlcolor: Black
    citecolor: Black
    link-citations: true
    # linestretch: 1.05
    include-in-header:
      # The \everydisplay thing makes all math blocks use \small font
      text: |
        \usepackage{mathtools}
        \everydisplay\expandafter{\the\everydisplay\small}
        \usepackage{float}
        \floatplacement{figure}{H}
        \floatplacement{table}{H}
        \usepackage{setspace}
        \pagenumbering{arabic}
        \usepackage{titlesec}
        \titleformat{\section}{\fontsize{12}{14}\bfseries}{\thesection}{1em}{}
        \titleformat{\subsection}{\fontsize{11}{14}\bfseries}{\thesubsection}{1em}{}
---
